universities

### 2020-08-23 inst/universities.Rmd
universities now named

H1 <- hyper2(pnames=c("AUT_pre",a[c(1:2,4:8),1]))
for(i in 2012:2016){
  b <- f(a,i)
  rownames(b)[3] <- "AUT_pre"
  H1 <- combine(H1,ordertable2supp(b))
} # column loop closes

H2 <- hyper2(pnames=c("AUT_post",a[c(1:2,4:8),1]))
for(i in 2017:2020){
  jj <- f(a,i)
  rownames(jj)[3] <- "AUT_post"
  H2 <- combine(H2,ordertable2supp(jj))
}
maxp(H2)
```

@@

```{r}
H <- combine(H1,H2)
maxp(H)
samep.test(H,c(1,9))
```

>>>>

H1 <- hyper2(pnames=c("AUT_pre",a[c(1:2,4:8),1]))
for(i in 2012:2016){
  b <- f(a,i)
  rownames(b)[3] <- "AUT_pre"
  H1 <- H1 + ordertable2supp(b)
} # column loop closes

H2 <- hyper2(pnames=c("AUT_post",a[c(1:2,4:8),1]))
for(i in 2017:2020){
  jj <- f(a,i)
  rownames(jj)[3] <- "AUT_post"
  H2 <- H2 + ordertable2supp(jj)
}
maxp(H2)
```

@@

```{r}
H <- H1 + H2
maxp(H)
samep.test(H,c(1,9))
```
